\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{hyperref}
\hypersetup{
    pdftitle={Omar Essam El-Din Mohamed's CV},
    pdfauthor={Omar Essam El-Din Mohamed},
    colorlinks=true,
    urlcolor=primaryColor
}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

% Section Formatting
\titleformat{\section}
{\normalfont\Large\bfseries\color{primaryColor}}
{\thesection}{1em}{}
\titlespacing*{\section}
{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\renewcommand{\sectionmark}[1]{\markboth{#1}{}}
% Add a horizontal rule after each section title
\titleformat{name=\section}
  {\normalfont\Large\bfseries\color{primaryColor}}
  {\thesection}{1em}{\color{primaryColor}\MakeUppercase{#1}\vspace{0.5ex}\titlerule}

\begin{document}
\begin{center}
    {\LARGE \textbf{Omar Essam El-Din Mohamed}} \\
    {Zahraa El Maadi, Cairo, Egypt} \\
    {\faPhone* \hspace{0.2cm} +20 1004819774} \hspace{1cm}
    {\href{mailto:eng.omar.e@gmail.com}{\faEnvelope[regular] \hspace{0.2cm} eng.omar.e@gmail.com}} \hspace{1cm}
            {\href{https://www.linkedin.com/in/omar-essam-b602279b}{\faLinkedin \hspace{0.2cm} LinkedIn}} \hspace{1cm}
    {\href{https://github.com/engomaressam}{\faGithub \hspace{0.2cm} GitHub}}
\end{center}

\section{Professional Summary}
A highly skilled Data Engineering And Machine Learning Lead with extensive experience in construction, civil engineering, data engineering, and machine learning. Currently specializing in AI development, web AI applications, and full-stack websites, with a proven track record of delivering innovative solutions like chatbots with local LLMs and running background commands with AI Agents to support company operations. Adept at leveraging advanced technologies, including GPU-accelerated development, to optimize workflows and enhance business insights under tight deadlines.

\section{Education}
\textbf{Cairo University}, Bachelor of Science in Civil Engineering, May 2013 \\
\textit{Overall Grade:} Good (C) \\
\textit{Project Grade:} Excellent (A) {Graduation Project:} Steel Bridges Design \\

\textbf{Orouba Language School}, Graduation Score: 98.9\% (405.5/410)

\section{Professional Experience}
\textbf{\textcolor{primaryColor}{Programming and Data Engineering Experience (6 years of experience)}}
\begin{itemize}[leftmargin=*]
    \item \textbf{Data Engineering And Machine Learning Lead} | Rowad Modern Engineering (Jan 2025 – Present)
    \begin{itemize}[leftmargin=1cm]
        \item Developed a Retrieval-Augmented Generation (RAG) chatbot using embeddings to enable efficient document-based question answering, improving internal knowledge access.
        \item Built a full-stack website integrating Oracle ERP and on-premises data warehouse, allowing users to extract data, query insights, and visualize results for enhanced decision-making.
        \item Leveraged NVIDIA 4090 GPUs to develop AI agents for automating coding, debugging, and workflow optimization, significantly improving team productivity.
    \end{itemize}
    \item \textbf{Data Engineering Lead} | Rowad Modern Engineering (Jul 2023 – Dec 2024)
    \begin{itemize}[leftmargin=1cm]
        \item Established a data warehouse team, integrated data sources for improved reporting and visualization.
    \end{itemize}
    \item \textbf{Data Scientist} | Rowad Modern Engineering (Jul 2021 – Dec 2022)
    \begin{itemize}[leftmargin=1cm]
        \item Developed machine learning models for cash flow predictions.
    \end{itemize}
    \item \textbf{Senior Data Engineer} | Rowad Modern Engineering (Nov 2020 – Jun 2021)
    \begin{itemize}[leftmargin=1cm]
        \item Automated repetitive tasks using Python, saving significant resource hours.
    \end{itemize}
    \item \textbf{IT Networking / Data Engineer} | Rowad Modern Engineering (Jan 2020 – Oct 2020)
    \begin{itemize}[leftmargin=1cm]
        \item Maintained MySQL databases on Linux Servers, ensuring seamless data access and storage.
    \end{itemize}
    \item \textbf{Co-Owner} | Cyber Cafe (2009 – 2011)
    \begin{itemize}[leftmargin=1cm]
        \item Managed hardware and networking for all systems.
    \end{itemize}
\end{itemize}

\newpage
\textbf{\textcolor{primaryColor}{Construction and Civil Engineering Experience (7 years of experience)}}
\begin{itemize}[leftmargin=*]
    \item \textbf{Project Control Section Head} | Rowad Modern Engineering, Bridges Sector (Sep 2019 – Dec 2020)
    \begin{itemize}[leftmargin=1cm]
        \item Managed the project control team for bridge projects. Streamlined cost and schedule reporting processes. Enhanced coordination between construction and planning teams.
    \end{itemize}
    \item \textbf{Senior Project Control Engineer} | Rowad Modern Engineering, Head Office (Jan 2017 – Aug 2019)
    \begin{itemize}[leftmargin=1cm]
        \item Oversaw multiple project schedules and cost control measures. Delivered periodic project performance reports to stakeholders.
    \end{itemize}
    \item \textbf{Project Control Engineer} | Rowad Modern Engineering (Apr 2016 – Dec 2016)
    \begin{itemize}[leftmargin=1cm]
        \item Worked on major infrastructure projects including Nefisha Bridge and El Sokhna Tunnel.
    \end{itemize}
    \item \textbf{Tendering Engineer} | Rowad Modern Engineering, Tender Department (Jan 2016 – Mar 2016)
    \begin{itemize}[leftmargin=1cm]
        \item Evaluated project tenders for technical and financial feasibility.
    \end{itemize}
    \item \textbf{Planning/Cost Control Engineer} | Concrete Plus (May 2011 – Aug 2013)
    \begin{itemize}[leftmargin=1cm]
        \item Coordinated cost control for multiple projects from the head office.
    \end{itemize}
    \item \textbf{Site Engineer} | Concrete Plus, Porto October Project (Aug 2010 – Aug 2011)
    \begin{itemize}[leftmargin=1cm]
        \item Supervised on-site construction activities, ensuring compliance with design specifications.
    \end{itemize}
\end{itemize}

\section{Key Skills}
\vspace{-1.5ex}
\begin{itemize}[leftmargin=*, itemsep=0.5ex]
    \item \textbf{Data Engineering:} \\
    ETL pipelines, Airflow, Spark, ERP systems, Docker
    \item \textbf{Machine Learning and AI:} \\
    RAG, embeddings, GPU-accelerated development (NVIDIA 4090), AI agent development
    \item \textbf{Data Visualization and BI Tools:} \\
    Power BI, Looker, Tableau, visualization libraries within Python
    \item \textbf{Engineering Tools:} \\
    Primavera P6, MS Project, Synchro, Revit, Navisworks, AutoCAD
    \item \textbf{Programming:} \\
    Python, SQL, Java, R, C++, C\# (familiar)
    \item \textbf{Software:} \\
    Microsoft Office, Adobe Photoshop, Illustrator, After Effects
    \item \textbf{Construction Expertise:} \\
    Cost Control, Tender Evaluation, Risk Management
    \item \textbf{Languages:} \\
    Arabic (Native), English (Fluent)
\end{itemize}

\newpage
\section{Certifications}
\vspace{-1ex}
\begin{itemize}[leftmargin=*, itemsep=0.5ex]
    \item Certified Data Scientist Professional (Epsilon AI)
    \item Primavera P6
    \item Python Programming
    \item PMP Certification
    \item CCNA and CCNP Networking
    \item Steel Bridges Design
    \item Develop Generative AI Applications: Get Started (IBM, Coursera, Jul 2025)
    \item Build RAG Applications: Get Started (IBM, Coursera, Jul 2025)
    \item Vector Databases for RAG: An Introduction (IBM, Coursera, Jul 2025)
\end{itemize}

\section{Personal Projects}
\vspace{-1ex}
\begin{itemize}[leftmargin=*, itemsep=0.5ex]
    \item Guitarist in an Iron Maiden cover band.
    \item Created a music YouTube channel with over 100,000 subscribers.
    \item Co-created the social media group ESS.
    \item Co-hosted a political podcast.
    \item Wrote two sci-fi novels.
    \item Worked in the rescue of street cats and dogs in Maadi.
\end{itemize}

\end{document}